Global code motion of congruent instructions

### 2017-09-16 cgo/paper.tex
plot instead of table for gcm metric

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{comment}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphviz}
\usepackage{auto-pst-pdf}
\usepackage{etoolbox}
\usepackage{flushend}
\usepackage{needspace}
\usepackage{algpseudocode}

@@

\begin{verbatim}
// Return true if the merge-set of source node of a visited J-edge (incoming edge of
// lnode) is not the subset of the merge-set of lnode.
bool still_inconsistent(Node lnode, JEdges JE, Visited V, MergeSet MergeSet)
  for e in (all incoming edges to lnode)
    if e is in JE and e in V
      if MergeSet(Source Node of e) is not a subset of MergeSet(lnode)
        return true
  return false
\end{verbatim}

@@

\begin{verbatim}
// Compute a merge-set top-down in breadth first order.
bool constructMergeSet_1(BFSList B, JEdges JE, DomLevel DL)
  repeat = false
  V = empty list of visited edges
  for n in B
    for e in (all incoming edges to n)
      if e is in JE and e not in V
        V(e) = true
        let tmp = Source Node of e
        let tnode = Target Node of e
        let lnode = NULL
        while (DL(tmp) >= DL(tnode))
          MergeSet(tmp) = MergeSet(tmp) U MergeSet(tnode) U {tnode}
          lnode = tmp
          tmp = dom-parent(tmp)
        repeat = still_inconsistent(lnode, JE, MergeSet)
  return repeat
\end{verbatim}
\newpage
\begin{verbatim}
// Construct merge-set of each node in Control-Flow-Graph G of a function.
void constructMergeSet(CFG G)
  B = Breadth First Order of G
  JE = JEdges of G
  DL = List of Path length (from root) of each node in G.
  do // Call until a fixed point is reached.
    Repeat = constructMergeSet_1(B, JE, DL)
  while (Repeat)
\end{verbatim}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & size reduction in Bytes & size reduction in Bytes\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544  \\\hline
401.bzip2	& 1.00  & -1600  & 128  \\\hline
403.gcc	        & 1.00  & -58176 & 3384 \\\hline
429.mcf	        & 1.03  & 160    & 16   \\\hline
433.milc	& 1.00  & -656   & 224  \\\hline
444.namd	& 1.00  & -3864  & -1168\\\hline
445.gobmk	& 0.99  & -20480 & -264 \\\hline
447.dealII	& 0.95  & -27836 & 50934\\\hline
450.soplex	& 0.99  & 2220   & 348  \\\hline
453.povray	& 0.97  & 164    & -472 \\\hline
456.hmmer	& 0.99  & -3464  & -352 \\\hline
458.sjeng	& 1.02  & 440    & 1456 \\\hline
462.libquantum	& 1.00  & -96    & 0    \\\hline
464.h264ref	& 1.00  & -3424  & 864  \\\hline
470.lbm	        & 1.00  & 0      & 0    \\\hline
471.omnetpp	& 1.00  & 2688   & 200  \\\hline
473.astar	& 1.00  & -928   & 152  \\\hline
482.sphinx3	& 0.99  & 3008   & -176 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}}
  \end{center}
  \caption{Execution time (ratio) and code size change (Bytes) with and without
    \gcm{} (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng;
    code size improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|r|r|r|}
      \hline
Number of spills  &base(-Ofast) &\GCM{}(-Ofast) &\%change (low better) \\\hline
400.perlbench	  & 2539	& 2493	& 0.98 \\\hline
401.bzip2	  & 718	        & 707	& 0.98 \\\hline
403.gcc	          & 5782	& 5722	& 0.99 \\\hline
429.mcf	          & 14	        & 17	& 1.21 \\\hline
433.milc	  & 635	        & 642	& 1.01 \\\hline
444.namd	  & 3223	& 3274	& 1.01 \\\hline
445.gobmk	  & 2166	& 2173	& 1.00 \\\hline
447.dealII	  & 11074	& 10234	& 0.92 \\\hline
450.soplex	  & 1122	& 1125	& 1.00 \\\hline
453.povray	  & 4701	& 4692	& 1.09 \\\hline
456.hmmer	  & 1197	& 1274	& 1.06 \\\hline
458.sjeng	  & 168	        & 176	& 1.05 \\\hline
462.libquantum	  & 118	        & 118	& 1.00 \\\hline
464.h264ref	  & 3379	& 3454	& 1.02 \\\hline
470.lbm	          & 33	        & 33	& 1.00 \\\hline
471.omnetpp	  & 524	        & 527	& 1.00 \\\hline
473.astar	  & 180	        & 201	& 1.12 \\\hline
482.sphinx3	  & 674	        & 670	& 0.99 \\\hline
483.xalancbmk	  & 5102	& 4965	& 0.97 \\\hline
Grand Total	  & 43349	& 42497	& 0.98 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Number of spills before and after \gcm{}(\GCM{}) on SPEC2006 at
    -Ofast. Spills reduced by 2\%.}
  \label{tab:spills}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|c|c|c|}
      \hline
  Benchmarks      &   Baseline	        & \GCM{}           & \%Decrease (low better) \\\hline
  400.perlbench	  &   186,829,426	& 184,690,006	& 0.99 \\\hline
  401.bzip2	  &   76,337,033	& 75,942,641	& 0.99 \\\hline
  403.gcc         &   1,079,625,231	& 1,073,158,220	& 0.99 \\\hline
  429.mcf         &   78,336,298	& 77,859,513	& 0.99 \\\hline
  433.milc	  &   272,525,306	& 269,684,876	& 0.99 \\\hline
  444.namd	  &   78,354,313	& 77,875,603	& 0.99 \\\hline
  445.gobmk	  &   261,229,078	& 258,459,798	& 0.99 \\\hline
  447.dealII	  &   643,457,797	& 638,628,331	& 0.99 \\\hline
  450.soplex	  &   245,442,755	& 242,811,500	& 0.99 \\\hline
  453.povray	  &   499,034,715	& 494,785,035	& 0.99 \\\hline
  456.hmmer	  &   214,425,324	& 211,984,389	& 0.99 \\\hline
  458.sjeng	  &   89,612,524	& 88,803,166	& 0.99 \\\hline
  462.libquantum  &   84,762,158	& 84,077,905	& 0.99 \\\hline
  464.h264ref	  &   151,049,588	& 149,284,624	& 0.99 \\\hline
  470.lbm         &   71,878,726	& 71,775,405	& 1.00 \\\hline
  471.omnetpp	  &   382,661,268	& 379,123,833	& 0.99 \\\hline
  473.astar	  &   78,351,117	& 77,872,820	& 0.99 \\\hline
  482.sphinx3	  &   158,434,290	& 156,586,406	& 0.99 \\\hline
  483.xalancbmk	  &   22,485,708,759	& 22,455,060,569& 1.00 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Change in total number of instructions executed during the
    compilation with and without \gcm{} (\GCM{}) on \SPEC{} at -Ofast. The
    instructions were counted using valgrind.}
  \label{tab:compile-time}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.8}{
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|r|r|r|r|}
      \hline
  &  \multicolumn{3}{|c|}{Hoisted by LICM} &\multicolumn{3}{|c|}{Sunk by LICM} &\multicolumn{3}{|c|}{Functions Inlined} &  \multicolumn{3}{|c|}{Functions Deleted} \\\hline
 Benchmarks          & Base        & \GCM{}	& \%  &Base     & \GCM{}   &\%    & Base	& \GCM{}	  &\%   & Base	& \GCM{}	& \% \\\hline
 400.perlbench	  & 2428	& 2480	& 2.1 & 36	& 35	& -2.8 & 1562	& 1565	  & 0.2 & 232	& 234	& 0.9  \\\hline
 401.bzip2	  & 721	        & 825	& 14.4& 3	& 3	& 0.0  & 172	& 180	  & 4.7 & 32	& 33	& 3.1  \\\hline
 403.gcc	  & 8867	& 10079	& 13.7& 143	& 182	& 27.3 & 5034	& 5080	  & 0.9 & 1303	& 130	& 0.1  \\\hline
 429.mcf	  & 55	        & 51	& -7.3& 1	& 1	& 0.0  & 4	& 4	  & 0.0 & 0 	& 0	& 0.0  \\\hline
 433.milc	  & 2537	& 2795	& 10.2& 3	& 3	& 0.0  & 75	& 81	  & 8.0 & 0	& 0	& 0.0  \\\hline
 444.namd	  & 2204	& 2206	& 0.1 & 240	& 240	& 0.0  & 387	& 390	  & 0.8 & 57	& 55	& -3.5 \\\hline
 445.gobmk	  & 3090	& 3107	& 0.6 & 18	& 19	& 5.6  & 735	& 775	  & 5.4 & 230	& 234	& 1.7  \\\hline
 447.dealII	  & 59114	& 95884	& 62.2& 60	& 8	& -86.7& 100891& 100692  & -0.2& 30219	& 29966	& -0.8 \\\hline
 450.soplex	  & 4668	& 4848	& 3.9 & 18	& 17	& -5.6 & 9801	& 9784	  & -0.2& 3125	& 3112	& -0.4 \\\hline
 453.povray	  & 9533	& 9079	& -4.8& 23	& 32	& 39.1 & 5522	& 5532	  & 0.2 & 1202	& 1201	& -0.1 \\\hline
 456.hmmer	  & 3200	& 3232	& 1.0 & 3	& 8	& 166.7& 562	& 562	  & 0.0 & 103	& 101	& -1.9 \\\hline
 458.sjeng	  & 400	        & 446	& 11.5& 0	& 0	& 0.0  & 127	& 135	  & 6.3 & 18	& 18	& 0.0  \\\hline
 462.libquantum   & 362	        & 386	& 6.6 & 0 	& 0	& 0.0  & 87	& 87	  & 0.0 & 21	& 21	& 0.0  \\\hline
 464.h264ref	  & 17075	& 17153	& 0.5 & 4	& 4	& 0.0  & 338	& 382	  & 13.0& 72	& 72	& 0.0  \\\hline
 470.lbm	  & 39	        & 39	& 0.0 & 0	& 0	& 0.0  & 13	& 13	  & 0.0 & 4	& 4	& 0.0  \\\hline
 471.omnetpp	  & 565	        & 661	& 17.0& 32	& 30	& -6.3 & 4790	& 4843	  & 1.1 & 1321	& 1316	& -0.4 \\\hline
 473.astar	  & 691	        & 754	& 9.1 & 0	& 0	& 0.0  & 359	& 363	  & 1.1 & 113	& 113	& 0.0  \\\hline
 482.sphinx3	  & 1599	& 1693	& 5.9 & 11	& 9	& -18.2& 198	& 194	  & -2.0& 53	& 53	& 0.0  \\\hline
 483.xalancbmk	  & 9997	& 11453	& 14.6& 56	& 54	& -3.6 & 69534	& 68839	  & -1.0& 29875	& 29519	& -1.2 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Static metrics before (Base) and after \gcm{} (\GCM{}) on
    \SPEC{} at -Ofast. The \% Column show percentage increase in metric
    w.r.t. Base. \GCM{} improves LICM and inlining.}
  \label{tab:stats}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.8}{
    \begin{tabular}{|l|r|r|r|r|r|r|r|r|r|}
      \hline
 \GCM{}  &\multicolumn{2}{|c|}{Total Instructions} &\multicolumn{2}{|c|}{Scalars}  & \multicolumn{2}{|c|}{Loads} & \multicolumn{1}{|c|}{Stores} &Calls   &Instructions    \\\hline
 metric           &  H          &R        &H      &R       &H           &R              &H=R    &H & sunk \\\hline
 400.perlbench	  &  2387	& 2456	  &  855  & 857	   & 1493	& 1560		& 38	& 1	& 4	        \\\hline
 401.bzip2	  &  176	& 300	  &  27	  & 27	   & 149	& 273		& 0	& 0 	& 0		\\\hline
 403.gcc	  &  5670	& 5761	  &  2558 & 2567   & 3109	& 3191		& 3	& 0	& 1	        \\\hline
 429.mcf	  &  42	        & 43	  &  5	  & 5	   & 37 	& 38		& 0	& 0 	& 0		\\\hline
 433.milc	  &  128	& 130	  &  10	  & 10	   & 117	& 119		& 0	& 1	& 0		\\\hline
 444.namd	  &  262	& 264	  &  113  & 113	   & 148	& 150		& 0	& 1	& 0		\\\hline
 445.gobmk	  &  1021	& 1052	  &  312  & 314	   & 705	& 734		& 3	& 1	& 1	        \\\hline
 447.dealII	  &  10455	& 12325	  &  4009 & 4063   & 6394	& 8210		& 20	& 32	& 0	        \\\hline
 450.soplex	  &  2389	& 2731	  &  927  & 1004   & 1437	& 1702		& 14	& 11	& 0	        \\\hline
 453.povray	  &  1967	& 2269	  &  560  & 590	   & 1389	& 1661		& 4	& 14	& 0	        \\\hline
 456.hmmer	  &  408	& 427	  &  82	  & 82	   & 319	& 338		& 1	& 6	& 0	        \\\hline
 458.sjeng	  &  372	& 399	  &  128  & 138	   & 234	& 251		& 1	& 9	& 1	        \\\hline
 462.libquantum	  &  49	        & 49	  &  17	  & 17	   & 32	      	& 32		& 0	& 0	& 0		\\\hline
 464.h264ref	  &  2953	& 3438	  &  712  & 779	   & 2238	& 2656		& 2	& 1	& 1	        \\\hline
 470.lbm	  &  23	        & 23	  &  4	  & 4	   & 19		& 19		& 0	& 0	& 0		\\\hline
 471.omnetpp	  &  391	& 408	  &  92	  & 92	   & 297	& 314		& 0	& 2	& 0		\\\hline
 473.astar	  &  202	& 222	  &  62	  & 64	   & 140	& 158		& 0	& 0	& 0		\\\hline
 482.sphinx3	  &  168	& 172	  &  32	  & 32	   & 136	& 140		& 0	& 0	& 0		\\\hline
 483.xalancbmk	  &  5894	& 6162	  &  2586 & 2660   & 3301	& 3495		& 4	& 3	& 2	        \\\hline
 Grand total      &34957	&38631	  &13091  &13418   &21694	&25041	        &90	&82     &10             \\\hline
    \end{tabular}}
  \end{center}
  \caption{\GCM{} stats on SPEC2006 at -Ofast, H(Hoisted,) R(Removed); Loads are
    hoisted the most followed by scalars, stores and calls.}
  \label{tab:code-motion-metric}
\end{table}

>>>>

%% Some recommended packages.
\usepackage{booktabs}   %% For formal tables:
                        %% http://ctan.org/pkg/booktabs
\usepackage{subcaption} %% For complex figures with subfigures/subcaptions
                        %% http://ctan.org/pkg/subcaption
\usepackage{comment}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{graphviz}
\usepackage{auto-pst-pdf}
\usepackage{etoolbox}
\usepackage{flushend}
\usepackage{needspace}
\usepackage{algpseudocode}
\usepackage[final]{pdfpages}

@@

\begin{verbatim}
// Return true if the merge-set of source node of a
// visited J-edge (incoming edge of lnode) is not
// the subset of the merge-set of lnode.
bool
still_inconsistent(Node lnode, JEdges JE,
                   Visited V, MergeSet MergeSet)
  for e in (all incoming edges to lnode):
    if e is in JE and e in V:
      if MergeSet(Source Node of e)
         is not a subset of MergeSet(lnode):
        return true
  return false
\end{verbatim}

@@

\begin{verbatim}
// Compute a merge-set breadth first order.
bool constructMergeSet_1(BFSList B, JEdges JE,
                         DomLevel DL)
  repeat = false
  V = empty list of visited edges
  for n in B:
    for e in (all incoming edges to n):
      if e is in JE and e not in V:
        V(e) = true
        let tmp = Source Node of e
        let tnode = Target Node of e
        let lnode = NULL
        while (DL(tmp) >= DL(tnode)):
          MergeSet(tmp) = MergeSet(tmp)
                          U MergeSet(tnode)
                          U {tnode}
          lnode = tmp
          tmp = dom-parent(tmp)
        repeat = still_inconsistent(lnode, JE, MergeSet)
  return repeat
\end{verbatim}
\newpage
\begin{verbatim}
// Construct merge-set of each node in
// Control-Flow-Graph G of a function.
void constructMergeSet(CFG G)
  B = Breadth First Order of G
  JE = JEdges of G
  DL = List of Path length (from root) of each node in G.
  do: // Call until a fixed point is reached.
    Repeat = constructMergeSet_1(B, JE, DL)
  while (Repeat)
\end{verbatim}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|c|c|c|}
      \hline
% TODO: Check if putting code-size or spills number is okay or only %age is required.
% llvm trunk vs. llvm trunk with code-motion
                &\% performance uplift & size reduction (Bytes) & size reduction (Bytes)\\
Benchmarks      & at -Ofast (high better)& at -Ofast (high better) & at -Os (high better)\\\hline
400.perlbench	& 1.00  & -9120  & 544  \\\hline
401.bzip2	& 1.00  & -1600  & 128  \\\hline
403.gcc	        & 1.00  & -58176 & 3384 \\\hline
429.mcf	        & 1.03  & 160    & 16   \\\hline
433.milc	& 1.00  & -656   & 224  \\\hline
444.namd	& 1.00  & -3864  & -1168\\\hline
445.gobmk	& 0.99  & -20480 & -264 \\\hline
447.dealII	& 0.95  & -27836 & 50934\\\hline
450.soplex	& 0.99  & 2220   & 348  \\\hline
453.povray	& 0.97  & 164    & -472 \\\hline
456.hmmer	& 0.99  & -3464  & -352 \\\hline
458.sjeng	& 1.02  & 440    & 1456 \\\hline
462.libquantum	& 1.00  & -96    & 0    \\\hline
464.h264ref	& 1.00  & -3424  & 864  \\\hline
470.lbm	        & 1.00  & 0      & 0    \\\hline
471.omnetpp	& 1.00  & 2688   & 200  \\\hline
473.astar	& 1.00  & -928   & 152  \\\hline
482.sphinx3	& 0.99  & 3008   & -176 \\\hline
483.xalancbmk	& 1.01  & 46492  & 4012 \\\hline
Geomean         & 0.997 &  & \\\hline
    \end{tabular}}
  \end{center}
  \caption{Execution time (ratio) and code size change (Bytes) with and without
    \gcm{} (\GCM{}) on \SPEC{}: performance uplift at -Ofast in mcf and sjeng;
    code size improvement in dealII at -Os.}
  \label{tab:code-size}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|r|r|r|}
      \hline
Number of spills  &base(-Ofast) &\GCM{}(-Ofast) &\%change\\\hline
400.perlbench	  & 2539	& 2493	& 0.98 \\\hline
401.bzip2	  & 718	        & 707	& 0.98 \\\hline
403.gcc	          & 5782	& 5722	& 0.99 \\\hline
429.mcf	          & 14	        & 17	& 1.21 \\\hline
433.milc	  & 635	        & 642	& 1.01 \\\hline
444.namd	  & 3223	& 3274	& 1.01 \\\hline
445.gobmk	  & 2166	& 2173	& 1.00 \\\hline
447.dealII	  & 11074	& 10234	& 0.92 \\\hline
450.soplex	  & 1122	& 1125	& 1.00 \\\hline
453.povray	  & 4701	& 4692	& 1.09 \\\hline
456.hmmer	  & 1197	& 1274	& 1.06 \\\hline
458.sjeng	  & 168	        & 176	& 1.05 \\\hline
462.libquantum	  & 118	        & 118	& 1.00 \\\hline
464.h264ref	  & 3379	& 3454	& 1.02 \\\hline
470.lbm	          & 33	        & 33	& 1.00 \\\hline
471.omnetpp	  & 524	        & 527	& 1.00 \\\hline
473.astar	  & 180	        & 201	& 1.12 \\\hline
482.sphinx3	  & 674	        & 670	& 0.99 \\\hline
483.xalancbmk	  & 5102	& 4965	& 0.97 \\\hline
Grand Total	  & 43349	& 42497	& 0.98 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Number of spills before and after \gcm{}(\GCM{}) on SPEC2006 at
    -Ofast. Lower is better in \%age change. Spills reduced by 2\%.}
  \label{tab:spills}
\end{table}

@@

\begin{table}[h]
  \begin{center}
    \scalebox{0.7}{
    \begin{tabular}{|l|c|c|c|}
      \hline
      Benchmarks      &   Baseline	        & \GCM{}           & \%Decrease\\
       & (in Millions)& (in Millions)& (lower is better)\\\hline
  400.perlbench	  &   186	& 184	& 0.99 \\\hline
  401.bzip2	  &   76	& 75	& 0.99 \\\hline
  403.gcc         &   1,079	& 1,073	& 0.99 \\\hline
  429.mcf         &   78	& 77	& 0.99 \\\hline
  433.milc	  &   272	& 269	& 0.99 \\\hline
  444.namd	  &   78	& 77	& 0.99 \\\hline
  445.gobmk	  &   261	& 258	& 0.99 \\\hline
  447.dealII	  &   643	& 638	& 0.99 \\\hline
  450.soplex	  &   245	& 242	& 0.99 \\\hline
  453.povray	  &   499	& 494	& 0.99 \\\hline
  456.hmmer	  &   214	& 211	& 0.99 \\\hline
  458.sjeng	  &   89	& 88	& 0.99 \\\hline
  462.libquantum  &   84	& 84	& 0.99 \\\hline
  464.h264ref	  &   151	& 149	& 0.99 \\\hline
  470.lbm         &   71	& 71	& 1.00 \\\hline
  471.omnetpp	  &   382	& 379	& 0.99 \\\hline
  473.astar	  &   78	& 77	& 0.99 \\\hline
  482.sphinx3	  &   158	& 156	& 0.99 \\\hline
  483.xalancbmk	  &   22,485	& 22,455& 1.00 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Change in total number of instructions executed during the
    compilation with and without \gcm{} (\GCM{}) on \SPEC{} at -Ofast. The
    instructions were counted using valgrind.}
  \label{tab:compile-time}
\end{table}

@@

\begin{table}[h!]
  \begin{center}
    \scalebox{0.8}{
    \begin{tabular}{|l|r|r|r|r|}
      \hline
      &\multicolumn{2}{|c|}{Loop Invariant Motion}  & \multicolumn{2}{|c|}{Functions} \\\hline
 Benchmarks       & Hoisted \% & Sunk \% &  Inlined\%   & Deleted\% \\\hline
 400.perlbench	  & 2.1 & -2.8 &  0.2 &  0.9  \\\hline
 401.bzip2	  & 14.4& 0.0  &  4.7 &  3.1  \\\hline
 403.gcc	  & 13.7& 27.3 &  0.9 &  0.1  \\\hline
 429.mcf	  & -7.3& 0.0  &  0.0 &  0.0  \\\hline
 433.milc	  & 10.2& 0.0  &  8.0 &  0.0  \\\hline
 444.namd	  & 0.1 & 0.0  &  0.8 &  -3.5 \\\hline
 445.gobmk	  & 0.6 & 5.6  &  5.4 &  1.7  \\\hline
 447.dealII	  & 62.2& -86.7& -0.2 &  -0.8 \\\hline
 450.soplex	  & 3.9 & -5.6 & -0.2 &  -0.4 \\\hline
 453.povray	  & -4.8& 39.1 &  0.2 &  -0.1 \\\hline
 456.hmmer	  & 1.0 & 166.7&  0.0 &  -1.9 \\\hline
 458.sjeng	  & 11.5& 0.0  &  6.3 &  0.0  \\\hline
 462.libquantum   & 6.6 & 0.0  &  0.0 &  0.0  \\\hline
 464.h264ref	  & 0.5 & 0.0  &  13.0&  0.0  \\\hline
 470.lbm	  & 0.0 & 0.0  &  0.0 &  0.0  \\\hline
 471.omnetpp	  & 17.0& -6.3 &  1.1 &  -0.4 \\\hline
 473.astar	  & 9.1 & 0.0  &  1.1 &  0.0  \\\hline
 482.sphinx3	  & 5.9 & -18.2&  -2.0&  0.0  \\\hline
 483.xalancbmk	  & 14.6& -3.6 &  -1.0&  -1.2 \\\hline
    \end{tabular}}
  \end{center}
  \caption{Change in the static compile time metrics w.r.t. \gcm{} (\GCM{}) on
    \SPEC{} at -Ofast. The \% columns show percentage increase in metric
    w.r.t. baseline. \GCM{} improves LICM and inlining in general.}
  \label{tab:stats}
\end{table}

@@

\begin{figure*}
\includegraphics[width=\textwidth,height=10cm]{gcm-stats.pdf}
\caption{\GCM{} stats on SPEC2006 at -Ofast. Loads are hoisted the most followed
  by scalars, stores and calls.}
\label{tab:code-motion-metric}
\end{figure*}
